%%%% LLARS Demo Paper - IJCAI-ECAI 2026

\typeout{LLARS Demo Paper for IJCAI-ECAI 2026}

\documentclass{article}
\pdfpagewidth=8.5in
\pdfpageheight=11in

\usepackage{ijcai26}
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}

\urlstyle{same}

\pdfinfo{
/TemplateVersion (IJCAI.2026.0)
}

\title{LLARS: A Platform for Evaluating LLM Outputs\\with Human and Machine Evaluators}

\author{
Philipp Steigerwald$^1$\and
Jens Albrecht$^1$\\
\affiliations
$^1$Technische Hochschule N\"urnberg Georg Simon Ohm, Germany\\
\emails
\{philipp.steigerwald, jens.albrecht\}@th-nuernberg.de
}

\begin{document}

\maketitle

\begin{abstract}
We demonstrate LLARS, an open-source platform that bridges the gap between domain experts and AI developers for systematic evaluation of LLM outputs.
The platform provides three integrated modules that can be used together or independently:
\textbf{Collaborative Prompt Engineering} enables real-time co-editing with character-level change tracking---useful for prompt optimization or compliance training under regulations like the EU AI Act~\cite{euaiact2024}.
\textbf{Batch Generation} scales output creation across multiple LLMs with cost tracking---enabling synthetic data generation or systematic model comparison.
\textbf{Large-Scale Evaluation} supports human and LLM evaluators with live agreement metrics---applicable to outputs from any source.
When combined, these modules form a complete pipeline from prompt development through rigorous assessment.
In a deployment evaluating counseling responses, this workflow improved human-LLM agreement by 12\%.

\vspace{0.3em}
\noindent\textbf{Demo:} \url{https://llars-project.github.io/demo}
\end{abstract}

\section{Introduction}

Evaluating Large Language Model (LLM) outputs requires collaboration between two groups with complementary expertise~\cite{chang2024survey}.
Domain experts---psychologists assessing counseling responses, physicians reviewing medical summaries, lawyers evaluating contract analysis---understand \emph{what} constitutes quality in their field.
AI developers understand \emph{how} to structure effective prompts and integrate LLM evaluators into production systems.
Yet current tools force these groups to work in isolation: annotation platforms like Label Studio~\cite{labelstudio2024} and Argilla~\cite{argilla2024} serve human annotators but lack LLM integration, while LLM-as-Judge frameworks like MT-Bench~\cite{zheng2024judging} require technical expertise and support only pairwise comparison.

LLARS bridges this gap by providing three integrated modules---\textbf{Prompt Engineering}, \textbf{Batch Generation}, and \textbf{Evaluation}---that form a complete pipeline when used together, yet each module can also operate independently for specific use cases.

\textbf{Collaborative Prompt Engineering.}
Domain experts and AI developers work together in a real-time collaborative workspace with full synchronization.
Character-level change tracking shows precisely who wrote or modified each part of the prompt, providing complete transparency over the evolution of evaluation criteria.
Each user can test the current prompt at any time in their own independent session---uploading real evaluation data and immediately observing how the production LLM interprets their criteria---without blocking other collaborators.
A full versioning system tracks prompt evolution, allowing teams to compare versions, identify which changes improved results, and roll back if needed.
When satisfied, domain experts export the finalized prompt as JSON, which AI developers download directly and integrate into their applications.
\emph{Standalone use:} Beyond prompt optimization, the collaborative workspace serves as a training environment where organizations document prompt engineering decisions with full attribution---relevant for compliance under the EU AI Act~\cite{euaiact2024}, which requires transparency in AI system development.

\textbf{Batch Generation.}
With prompts refined, teams use Batch Generation to create outputs at scale.
This module bridges prompt engineering and evaluation by automatically generating all combinations of evaluation items, prompt templates, and LLM models---a matrix approach that enables systematic comparison.
Users select data sources (existing scenarios, uploaded files, or custom inputs), choose one or more prompts, and specify which LLMs to test.
The system estimates costs before execution, tracks progress in real-time via WebSocket updates, and enforces optional budget limits.
Generated outputs can be exported as CSV or JSON, or directly converted into evaluation scenarios.
\emph{Standalone use:} Teams with existing prompts can use Batch Generation independently to create synthetic training data for model fine-tuning, generate test datasets for quality assurance, or produce content at scale for downstream applications.

\textbf{Large-Scale Evaluation.}
With outputs generated---or imported from external sources---teams conduct systematic evaluation.
This module enables comparison across different LLMs or parameter settings, testing whether smaller, cheaper models perform adequately.
For evaluation tasks, ranking outputs often provides more informative results than absolute rating, as relative comparison is easier for humans to judge consistently~\cite{steigerwald2025subjectline}.
Human evaluation remains the gold standard, but domain experts' time is limited.
LLM evaluators provide a cost-effective alternative for initial assessment; the ideal configuration combines both.
LLARS computes agreement across all evaluator combinations in real-time: human-human, LLM-LLM, and human-LLM, with metrics including Krippendorff's $\alpha$, Cohen's $\kappa$, and correlation coefficients.
\emph{Standalone use:} Teams can import existing outputs---from production systems, competitor analyses, or research datasets---directly into the evaluation module without using LLARS's other components.

An AI-assisted \textbf{Scenario Wizard} supports transitions between modules by analyzing uploaded datasets, suggesting appropriate evaluation types (rating, ranking, labeling), and proposing field mappings to LLARS's internal format.

This modular design addresses a fundamental challenge: domain experts know what matters but struggle to express it in prompts that LLMs interpret correctly, while AI developers can write effective prompts but lack the domain knowledge to capture subtle quality distinctions.
LLARS brings both groups into a shared environment where they iterate together---from initial prompt development through batch generation to rigorous evaluation---until criteria are properly captured and validated at scale.

\section{System Overview}

LLARS follows a microservices architecture (Figure~\ref{fig:architecture}) designed for real-time collaboration and scalable LLM evaluation.

\begin{figure}[t]
\centering
\resizebox{0.95\linewidth}{!}{%
\begin{tikzpicture}[
    node distance=0.35cm and 0.25cm,
    box/.style={rectangle, draw, rounded corners=2pt, minimum height=0.5cm, minimum width=1.3cm, font=\scriptsize\sffamily, align=center, fill=white},
    dbbox/.style={box, fill=gray!15},
    extbox/.style={box, fill=blue!8, draw=blue!40},
    biarrow/.style={{Stealth[length=1.5mm]}-{Stealth[length=1.5mm]}, thick, gray!70},
]
\node[box, fill=green!10] (human) {Domain Experts\\(Web UI)};
\node[box, fill=blue!10, right=1.2cm of human] (ai) {AI Developers\\(Web UI)};
\node[box, fill=cyan!12, below=0.5cm of human] (vue) {Vue.js Frontend};
\node[box, fill=purple!12, below=0.5cm of ai] (yjs) {Yjs Collab\\Server};
\node[box, fill=yellow!15, below right=0.5cm and -0.3cm of vue, minimum width=1.8cm] (flask) {Flask Backend};
\node[dbbox, below left=0.4cm and 0cm of flask] (db) {MariaDB};
\node[extbox, below right=0.4cm and 0cm of flask] (llm) {LiteLLM\\(100+ Models)};
\draw[biarrow] (human) -- (vue);
\draw[biarrow] (ai) -- (yjs);
\draw[biarrow] (vue) -- (flask);
\draw[biarrow] (yjs) -- (flask);
\draw[biarrow] (flask) -- (db);
\draw[biarrow] (flask) -- (llm);
\end{tikzpicture}%
}
\caption{LLARS architecture. Domain experts and AI developers collaborate via Vue.js frontend and Yjs real-time synchronization. LiteLLM enables testing with 100+ LLM providers.}
\label{fig:architecture}
\end{figure}

The Vue.js frontend provides evaluation interfaces, while a Yjs server~\cite{shapiro2011crdt} enables real-time collaborative editing with conflict-free synchronization.
The Flask backend orchestrates workflows and integrates with 100+ models via LiteLLM---GPT-4, Claude, Gemini, and local deployments via Ollama.

\section{Collaborative Prompt Engineering}

The first module provides a collaborative prompt engineering workspace (Figure~\ref{fig:collab}) where domain experts and AI developers jointly develop prompts with full real-time synchronization.

\begin{figure}[t]
\centering
\begin{tikzpicture}
\node[draw, rounded corners, fill=gray!5, minimum width=0.93\linewidth, minimum height=3.5cm, align=center] {
\begin{minipage}{0.85\linewidth}
\centering
\scriptsize\sffamily
\textbf{[Screenshot: Collaborative Prompt Engineering]}\\[0.3em]
\textit{Real-time editing with character-level tracking}\\[0.2em]
\textcolor{blue!70}{$\blacktriangleright$ Dr.\ Smith (Psychologist)} \quad \textcolor{green!70}{$\blacktriangleright$ J.\ Dev (Engineer)}\\[0.2em]
\textcolor{gray}{``Rate empathy on 1-5, where 5 means...''}\\
\textcolor{gray}{[Test Now] [Upload Data] [Export JSON] [History]}
\end{minipage}
};
\end{tikzpicture}
\caption{Collaborative workspace with character-level change tracking. Each user can test independently while others continue editing.}
\label{fig:collab}
\end{figure}

\textbf{Real-Time Collaboration:} Multiple users edit prompts simultaneously with CRDT-based synchronization.
Character-level change tracking shows exactly who wrote or modified each part---providing full attribution over the evolution of prompt criteria.
This transparency is valuable not only for iterative refinement but also for compliance documentation: organizations can demonstrate who contributed which evaluation criteria and when changes were made.

\textbf{Independent Testing:} Each user can test the current prompt at any time in their own session without blocking others.
Domain experts upload real data directly in the workspace and immediately see how the production LLM interprets their criteria.
This tight feedback loop enables rapid iteration until alignment is achieved.

\textbf{Version Control \& Export:} A full versioning system tracks prompt evolution, allowing teams to compare versions and roll back if needed.
Finalized prompts are exported as JSON for direct integration into applications---or archived as documentation for audit purposes.

\textbf{Standalone Use:} Beyond the evaluation pipeline, this module serves as a training environment where organizations teach prompt engineering practices.
The EU AI Act~\cite{euaiact2024} emphasizes transparency and human oversight in AI systems; LLARS's attribution tracking and version history support compliance by documenting how evaluation criteria were developed and by whom.

\section{Batch Generation}

The second module bridges prompt engineering and evaluation by automating output creation at scale.
Rather than manually testing individual prompts, teams define a generation matrix: all combinations of evaluation items, prompt templates, and LLM models are processed automatically.

\textbf{Matrix Generation:} Users configure jobs through a guided wizard, selecting data sources (scenarios, uploaded files, or custom inputs), prompt templates, and target LLMs.
The system generates outputs for every combination: $N$ items $\times$ $M$ prompts $\times$ $K$ models.
An AI-assisted Scenario Wizard analyzes uploaded datasets, suggests appropriate configurations, and maps fields to LLARS's internal format.

\textbf{Cost Control:} Before execution, LLARS estimates total cost based on token counts and model pricing.
Users can set budget limits; jobs automatically pause if costs exceed thresholds.
Real-time tracking via WebSocket shows progress, token usage, and accumulated costs.

\textbf{Pipeline Integration:} Generated outputs maintain full provenance---source item, prompt template, and model for each result.
Outputs transition seamlessly to evaluation: a team can generate 500 outputs across 3 models in the morning and have human evaluators rating them by afternoon.

\textbf{Standalone Use:} Teams with existing prompts can use Batch Generation independently.
Key use cases include: (1) \emph{Synthetic data generation} for model fine-tuning, where domain-specific prompts produce training examples at scale; (2) \emph{Test dataset creation} for QA pipelines, generating edge cases and regression tests; (3) \emph{Model screening} to quickly compare whether smaller, cheaper models produce acceptable outputs before investing in dedicated prompt optimization.

\section{Large-Scale Evaluation}

The third module enables systematic evaluation of LLM outputs---whether generated through Batch Generation or imported from external sources.

\textbf{Model Comparison:} Teams evaluate outputs across different LLMs, comparing GPT-4 against Claude or testing whether smaller models perform adequately.
This is particularly relevant when switching production LLMs or evaluating open-source alternatives to commercial APIs.

\textbf{Rating and Ranking:} LLARS supports multiple evaluation paradigms.
Ranking outputs is often more informative than absolute rating, as relative comparison is easier for humans to judge consistently~\cite{steigerwald2025subjectline}.
Rating provides absolute scores useful for threshold-based decisions.

\textbf{Human and LLM Evaluators:} Human evaluation remains the gold standard, but domain experts' time is scarce.
LLM evaluators provide a cost-effective alternative for initial assessment; the ideal configuration combines both, with human evaluators establishing ground truth while LLM evaluators scale assessment.

\textbf{Live Agreement Metrics:} LLARS computes agreement across all evaluator combinations in real-time: human-human (inter-annotator reliability), LLM-LLM (model consistency), and human-LLM (alignment between machine and human judgment).
Metrics include Krippendorff's $\alpha$, Cohen's $\kappa$, Fleiss' $\kappa$, Spearman's $\rho$, Kendall's $\tau$, and ICC.
Scenario owners see these metrics live, immediately identifying where human-machine disagreement reveals systematic biases.

\textbf{Standalone Use:} Teams can import existing outputs directly into the evaluation module without using LLARS's other components.
Use cases include: (1) \emph{Production monitoring}, evaluating outputs from deployed systems; (2) \emph{Competitor analysis}, systematically comparing outputs from different vendors; (3) \emph{Research datasets}, applying consistent evaluation criteria to existing corpora from prior studies.

\section{Application: Counseling Evaluation}

We deployed LLARS to evaluate LLM-generated responses for online mental health counseling~\cite{steigerwald2025caia}, demonstrating the complete pipeline.

\textbf{Prompt Engineering:} Psychology students and AI developers collaborated in the prompt workspace to define evaluation criteria for empathy, clarity, professionalism, and helpfulness.
Students uploaded real counseling exchanges and tested iteratively until the LLM's interpretations matched their expert judgment.
The character-level attribution documented each student's contributions---useful for academic credit and methodology documentation.

\textbf{Batch Generation:} Using the refined prompts, we generated evaluation outputs across GPT-4 and Claude-3 for 600 counseling responses, with real-time cost tracking ensuring budget compliance.

\textbf{Large-Scale Evaluation:} Five psychology students and the two LLM evaluators then rated the generated outputs.
Over four weeks, we collected 2,400 ratings.
Human agreement ranged from $\alpha = 0.61$ to $0.78$.
Initial human-LLM correlation was $r = 0.47$---LLMs rated empathy higher.
After three collaborative refinement iterations (returning to prompt engineering with insights from evaluation), agreement improved to $r = 0.54$ (12\% increase).

\section{Demonstration}

Our demonstration covers the complete workflow:
\begin{enumerate}
    \item \textbf{Prompt Engineering:} Collaboratively develop evaluation criteria with real-time editing and character-level tracking
    \item \textbf{Scenario Setup:} Use the AI-assisted wizard to configure evaluation type and map data fields
    \item \textbf{Batch Generation:} Generate outputs across multiple LLMs with real-time cost tracking
    \item \textbf{Evaluation:} Rate or rank outputs through human interface and parallel LLM assessment
    \item \textbf{Agreement Analysis:} Compare human-human, human-LLM, and LLM-LLM metrics live
\end{enumerate}

Attendees can evaluate provided examples or upload their own data.
LLARS is open-source (MIT), requiring Docker, 16GB RAM, 4+ CPU cores.

\vspace{0.3em}
\noindent\textbf{Repository:} \url{https://github.com/llars-project/llars}\\
\textbf{Documentation:} \url{https://llars-project.github.io}

\bibliographystyle{named}
\bibliography{llars}

\end{document}
